Papers

### 2023-01-18 papers.qmd
update slides

## Invited Talks
"Elastic Functional Data Analysis", *SMU Statistical Colloquium*, November 4, 2022

@@

"Alignment and Analysis of Proteomics Data using Square Root Slope Function Framework'', *CTW: Statistics of Time Warpings and Phase Variations 2012*, OSU MBI, Nov 7, 2012 [PDF](Presentations/MBI2012_Tucker.pdf)

"Statistical Analysis and Modeling of Elastic Functions'', *Department of Mathematical and Statistical Sciences, University of Alberta*, Aug 23, 2011. (Organizer: Yau Shu Wong) [PDF](Presentations/UA-Function_Warping.pdf)

>>>>

## Invited Talks
"Elasic Bayesian Model Calibration" *FSU Shape Group Statistical Meeting*, January 24, 2023, [Slides](https://jdtuck.github.io/presentations/FSU_Jan23/FSU_Jan23.html)

"Elastic Functional Data Analysis", *SMU Statistical Colloquium*, November 4, 2022, [Slides](Presentations/2022SMU_Nov_22.pdf)

@@

"Alignment and Analysis of Proteomics Data using Square Root Slope Function Framework'', *CTW: Statistics of Time Warpings and Phase Variations 2012*, OSU MBI, Nov 7, 2012 [Slides](Presentations/MBI2012_Tucker.pdf)

"Statistical Analysis and Modeling of Elastic Functions'', *Department of Mathematical and Statistical Sciences, University of Alberta*, Aug 23, 2011. (Organizer: Yau Shu Wong) [Slides](Presentations/UA-Function_Warping.pdf)
